Hello, world.
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

\title{Game Development Platform}
\author{}
\date{}

\begin{document}

\maketitle

\section{Profile}

\subsection{Introduction}
Game development requires programmers to either learn how to use a complex game engine or low level programming languages. Our solution aims to provide new game developers with a platform where they spend more time developing a game than managing graphics or I/O.

\subsection{Problem Description}
Game development requires the usage of low level programming languages or complicated game engines. There is a need for a high level programming language that can be used to develop games without having to manage input device peripherals or a graphical user interface.

\section{Objectives}

\subsection{General Objective}
Create a software solution, a platform that allows high level language programmers to develop games without worrying about a graphic user interface or I/O and instead spend more time developing the game.

\subsection{Specific Objectives}
\begin{itemize}
    \item Example games:
    \begin{itemize}
        \item A simple tic-tac-toe \href{https://docs.google.com/document/d/1MvlmgCBZvRrT61A3mnra-3bZ41zCcE_vmNHpHkZyQ2M/edit}{PRD Tictactoe}
        \item A generic Pac-Man \href{https://docs.google.com/document/d/1ST29Ap_2OGVEf--gPTfHYmAZrcIQC6jl6y32fM3UQWo/edit}{PRD Pacman}
    \end{itemize}
    \item Input peripherals support
    \begin{itemize}
        \item Keyboard
        \item Mouse
    \end{itemize}
    \item Output support
    \begin{itemize}
        \item Audio
        \item Graphical User Interface
    \end{itemize}
    \item Game Development Library
    \begin{itemize}
        \item This library will provide necessary tools for game development.
    \end{itemize}
\end{itemize}

\section{Scope and Limits}

\subsection{Scope}
\begin{itemize}
    \item Java developers that want to develop games.
\end{itemize}

\subsection{Limits}
\begin{itemize}
    \item Hardware
    \begin{itemize}
        \item A GPU that supports Vulkan, since version 1.3
    \end{itemize}
    \item Miscellany
    \begin{itemize}
        \item Games only can be played locally.
        \item Only 2D graphics.
        \item To run the game, the end-user has to have basic terminal knowledge.
        \item The library will be written in Java 17.
    \end{itemize}
\end{itemize}

\end{document}
