\subsection{Sprint 6}

\subsubsection{Introduction}
During sprint 6 the team focused on refactoring the script with the latest architecture, and refactor socket for screen, and finishing the US related to the pacman game. 

\subsubsection{Spikes}

\begin{itemize}
    \item Refactor script update with latests architecture: \href{https://tree.taiga.io/project/joseluis-teran-coffeetime/us/215?milestone=396824}{US id-215}
    \item Refactor socket client for screen bassed on latest architecture: \href{https://tree.taiga.io/project/joseluis-teran-coffeetime/us/216?milestone=397461}{US id-216}
\end{itemize}

\subsubsection{POCs}

No proofs of concept (POCs) were conducted in this sprint.

\subsubsection{Technical Justification}
In Sprint 6 the decision was made to refactor the script update and priorize US of pacman. The decision was made based on the following:

\begin{itemize}
    \item  Being able to execute the game. 
    \item  Terminate the US of pacman that were in carry over in order to finish pacman game.
\end{itemize}

\newpage

\subsubsection{Product Backlog}

\paragraph{Done}
Completed spikes.

\begin{itemize}
    \item Refactor script update with latests architecture: \href{https://tree.taiga.io/project/joseluis-teran-coffeetime/us/215?milestone=396824}{US id-215}
    \item Game communication: \href{https://tree.taiga.io/project/joseluis-teran-coffeetime/us/130?milestone=396824}{US id-130}
    \item US: bridge screen communication: \href{https://tree.taiga.io/project/joseluis-teran-coffeetime/us/135?milestone=396824}{US id-135}
    \item Game loop conditions: \href{https://tree.taiga.io/project/joseluis-teran-coffeetime/us/166?milestone=396824}{US id-166}
    \item  Colisions on Pacman Game: \href{https://tree.taiga.io/project/joseluis-teran-coffeetime/us/124?milestone=396824}{US id-124}
    \item  Pacman Collectables: \href{https://tree.taiga.io/project/joseluis-teran-coffeetime/us/80?milestone=396824}{US id-80}
    \item  Pacman Game Refactor: \href{https://tree.taiga.io/project/joseluis-teran-coffeetime/us/236?milestone=396824}{US id-236}
\end{itemize}

\paragraph{Carry Overs}
\begin{itemize}
    \item Refactor socket client for screen bassed on latest architecture: \href{https://tree.taiga.io/project/joseluis-teran-coffeetime/us/216?milestone=397461}{US id-216}
    \item Tic Tac Toe Game Implementation: \href{https://tree.taiga.io/project/joseluis-teran-coffeetime/us/25?milestone=397461}{US id-25}
    \item US: Pacman game initialize: \href{https://tree.taiga.io/project/joseluis-teran-coffeetime/us/110?milestone=397461}{US id-110}
\end{itemize}

\subsubsection{Impediments}
For the impediments we registered on the following link:

\href{https://docs.google.com/spreadsheets/d/16zbS6L_JsIA9JhoJ1_e8Luk3MzKs8KApNbeizERjYn0/edit?usp=sharing}{impediments}

\subsubsection{Conclusions}
For this sprint our goal was the refactoring of both the script and the socket, at the same time to document all the sprints and finish the US of pacman, the goal was not met in its entirety since it was not possible to finish the entire US of pacman and the socket refactor. 

\subsubsection{action items}

\begin{itemize}
    \item Fast and concrete code reviews.
    \item Self management at assigning US or tasks.
    \item Improve our US creation in product backlog.
\end{itemize}


\subsubsection{Epics}

For Sprint 6, we have the following epics:

\begin{itemize}
    \item Refactor script
    \item Refactor socket
    \item Pacman Game
    \item Tic Tac Toe Game
\end{itemize}