\subsection{Sprint 4}

\subsubsection{Introduction}
During sprint 4, the team focused on improving the library and addressing bugs and needs related to the Pacman game.

\subsubsection{Spikes}

No spikes were conducted in this sprint.

\subsubsection{POCs}

No proofs of concept (POCs) were conducted in this sprint.

\subsubsection{Technical Justification}
The decision was made to improve and develop the library prioritizing the Pacman game. The decision was based on the following:

\begin{itemize}
    \item Being able to develop the Pacman game.
    \item Finish Pacman enemies.
\end{itemize}

\newpage

\subsubsection{Product Backlog}

\paragraph{Done}
Completed user stories and tasks.

\begin{itemize}
    \item Implementation of render handler: \href{https://tree.taiga.io/project/joseluis-teran-coffeetime/us/88?milestone=394885}{US id-88}
    \item Game Graphics Management: \href{https://tree.taiga.io/project/joseluis-teran-coffeetime/us/87?milestone=394885}{US id-87}
    \item Pacman enemies: \href{https://tree.taiga.io/project/joseluis-teran-coffeetime/us/81?milestone=394885}{US id-81}
\end{itemize}

\paragraph{Carry Overs}
\begin{itemize}
    \item Tic Tac Toe Game: \href{https://tree.taiga.io/project/joseluis-teran-coffeetime/us/25?milestone=395911}{US id-25}
    \item UML Pacman Game: \href{https://tree.taiga.io/project/joseluis-teran-coffeetime/us/72?milestone=395911}{US id-72}
\end{itemize}

\subsection{Impediments}
For the impediments we registered on the following link:

\href{https://docs.google.com/spreadsheets/d/1v_3SvV4162Al9MyRWZ77Oe7ui-eKSd0T5Xl1QH822uc/edit?gid=0#gid=0}{impediments}

\subsection{Conclusions}
For this sprint, our goal was to improve the library and develop features that needs to be related to the Pacman game. The focus was on developing the Pacman game and finishing the implementation of Pacman enemies. The goal was partially met as some tasks were carried over to the next sprint.

\subsubsection{action items}

\begin{itemize}
    \item Fast and concrete code reviews.
    \item Improve our US creation in product backlog.
\end{itemize}

\subsubsection{Epics}

For Sprint 4, we have the following epics:

\begin{itemize}
    \item Implementation of render handler
    \item Pacman Enemies
\end{itemize}
